\section{Some intersection-theoretic lemmas}\label{appendix:intersection}

In this appendix we explicitly define the \emph{diagonal pull-back} along a morphism whose target is unobstructed (used in \cite{Ga}) and verify that this agrees with the virtual pull-back of \cite{Manolache-Pull} when both are defined. We also check that it satisfies some expected compatibility properties.

Consider a morphism of DM stacks $f\colon Y\to X$ over a smooth base $\mathfrak M$, such that $X$ is smooth over $\mathfrak M$ and $Y$ carries a virtual class given by a perfect obstruction theory $\EE_{Y/\mathfrak M}$. Then, for every Cartesian diagram
 \bcd
 G\ar[r,"g"]\ar[d,"q"]\ar[rd,phantom,"\Box"] & F\ar[d,"p"] \\
 Y\ar[r,"f"] & X 
 \ecd
and every class $\alpha\in \Achow_*(F)$, we may define
\[
 f^!_{\Delta}(\alpha)=\Delta_X^!([Y]^\text{vir}\times\alpha)\in \Achow_*(G)
\]
which we call the \emph{diagonal (virtual) pull-back}. We first show that it coincides with the usual virtual pull-back along $f$ in the presence of a compatible perfect obstruction theory for $f$.

\begin{lemma}\label{lem:diagonal_virtual_coincide}
Assume that there exists a relative obstruction theory $\EE_f$ compatible with $\EE_{Y/\mathfrak M}$ and the standard (unobstructed) obstruction theory for $X$, i.e:
 \bcd
 f^* \LL_{X/\mathfrak M} \ar[r] \ar[d,"\operatorname{Id}"] & \EE_{Y/\mathfrak M} \ar[r] \ar[d] & \EE_f \ar[r,"{[1]}"] \ar[d] & \, \\
 f^* \LL_{X/\mathfrak M} \ar[r] & \LL_{Y/\mathfrak M} \ar[r] & \LL_f \ar[r,"{[1]}"] & \,
 \ecd
 Then for every Cartesian diagram and every class $\alpha\in \Achow_*(F)$ as above,
 \[
  f^!_{\operatorname{v}}(\alpha)=f^!_\Delta(\alpha).
 \]
\end{lemma}
\begin{proof}

Consider the following cartesian diagram:
\bcd
G \ar[r,"q \times g"] \ar[d,"g"] \ar[rd,phantom,"\square"] & Y\times_{\mathfrak M}F \ar[r,"\pr_1"] \ar[d,"f \times \Id"] \ar[rd,phantom,"\square"] & Y \ar[d,"f"] \\
F \ar[r,"p \times \Id"] \ar[d,"p"] \ar[rd,phantom,"\square"] & X\times_{\mathfrak M} F \ar[r,"\pr_1"] \ar[d,"\Id \times p"] & X \\
X \ar[r,"\Delta_X"] & X\times_{\mathfrak M}X &
\ecd
Then, by commutativity of virtual pull-backs, we have
\begin{align*} \Delta_X^!([Y]^\text{vir}\times\alpha) & = \Delta^!((f^!_{\operatorname{v}}[X])\times\alpha) \\
& = \Delta_X^!(f^!_{\operatorname{v}}([X]\times\alpha)) \\
& = f^!_{\operatorname{v}}(\Delta_X^!([X]\times\alpha)) \\
& = f^!_{\operatorname{v}}(\alpha)
\end{align*}
as required.
\end{proof}

Secondly, we show that the \emph{diagonal} virtual pull-back behaves similarly to an ordinary virtual pull-back (e.g. commutes with other virtual pull-backs) even in the absence of a compatible perfect obstruction theory.

\begin{lemma} The \emph{diagonal} virtual pull-back morphism as defined above commutes with ordinary Gysin maps and with virtual pull-backs. \end{lemma}
\begin{proof} First consider the case of ordinary Gysin maps. We must consider a cartesian diagram:
\bcd
Y^{\prime \prime} \ar[r] \ar[d] \ar[rd,phantom,"\square"] & X^{\prime \prime} \ar[r] \ar[d] \ar[rd,phantom,"\square"] & S \ar[d,"k"] \\
Y^\prime \ar[r] \ar[d] \ar[rd,phantom,"\square"] & X^\prime \ar[r] \ar[d] & T \\
Y \ar[r,"f"] & X
\ecd
with $k$ a regular embedding and $f\colon Y\to X$ as before. We need to show that for all $\alpha \in A_*(X^\prime)$:
\begin{equation*} k^! f_{\Delta}^!(\alpha) = f^!_{\Delta} k^!(\alpha) \end{equation*}
We form the cartesian diagram:
\bcd
Y^{\prime \prime} \ar[r] \ar[d] \ar[rd,phantom,"\square"] & Y\times X^{\prime \prime} \ar[r] \ar[d] \ar[rd,phantom,"\square"] & S \ar[d,"k"] \\
Y^\prime \ar[r] \ar[d] \ar[rd,phantom,"\square"] & Y\times X^\prime \ar[r] \ar[d] & T \\
X \ar[r,"\Delta_X"] & X\times X &
\ecd
And apply commutativity of usual Gysin morphisms. In the case where $k$ is not a regular embedding but rather is equipped with a relative perfect obstruction theory, the same argument works with $k^!$ replaced by $k_{\text{v}}^!$.
\end{proof}